% Purpose: an example .tex file for the thesis.

\documentclass[11pt,leqno]{report}

\usepackage{ur_thesis}
\usepackage{times}
\usepackage{hyperref}
\usepackage{xcolor}		% make links dark blue
\definecolor{darkblue}{rgb}{0, 0, 0.5}
\hypersetup{colorlinks=true,citecolor=darkblue, linkcolor=darkblue, urlcolor=darkblue}
  
% citation style can be whatever is "accepted in your field"
\usepackage[round]{natbib}

\begin{document}

\sloppy
\title{Hast Thou Slain the Jabberwock?}
\author{Guillaume SANCHEZ}
\thesissupervisor{Frédéric BOUCHARA, Vincente GUIS, Ricard MARXER}
\thesisdepartment{Laboratoire Informatique et Systèmes}
\maketitle

% Feb 24, 2010 vandurme> the graduate office wanted a "ii" on the top right
% corner of the dedication page (lowercase Roman numeral page numbering), which
% explains the slightly messy tex code for this page:

%%%dedication page
\thispagestyle{empty}
%\thispagestyle{plain}
\newenvironment{dedication}
{\cleardoublepage \thispagestyle{empty} \vspace*{\stretch{1}}
  \begin{center} \em}
  {\end{center} \vspace*{\stretch{3}} }
\begin{dedication}

  %% To ... 

\end{dedication}

%%% CV page
\begin{curriculumvitae}

  Previous degrees and experience.

\end{curriculumvitae}

\begin{acknowledgments}

  Thanks to collaborators and supporters.

  %% Additional personal acknowledgments ...

 
\end{acknowledgments}

\begin{abstract}

  A brief summary.
  
\end{abstract}



\begin{contributors}

This work was supervised by a dissertation committee consisting of Professors
X, Y, and Z. 
This material is based upon work supported by the National Science Foundation Award
XXXXXXX.  Any opinions, findings, and conclusions or recommendations
expressed in this material are those of the author and do not necessarily
reflect the views of above named organization.

\end{contributors}


\tableofcontents
\listoftables
\listoffigures

\chapter{Introduction}

\chapter{Latex Tips}

\section{Citations}

This template uses the \verb|natbib|
package.
Use the command \verb|\cite| for citations in parentheses.
Use the command \verb|\citet| for citations in text.
Use the command \verb|\citeyearpar| for the year only, in parentheses.
For example,
\begin{verbatim}
    ... as in \LaTeX\ \cite{Lamport86} ...
    ... and \citet{Knuth86} claims ...
    ... and Knuth's later work \citeyearpar{Knuth86} claims ...
\end{verbatim}
will result in
\begin{quote}
... as in \LaTeX\ \cite{Lamport86} ...\\
... and \citet{Knuth86} claims ...\\
... and Knuth's later work \citeyearpar{Knuth86} claims ...
\end{quote}

You can change the template to use another citation style if you prefer.  The only requirement is that citations appear in the style ``accepted in your field.''

\section{Math}

Use \verb|\log| and \verb|\exp|, not \verb|log| and \verb|exp|.

Blank lines start a new paragraph - don't start
a new paragraph after an equation in the middle of a sentence.
Use
\begin{verbatim}
\[ e^{\pi i} = -1 \]
where $i=\sqrt{-1}.$ 
\end{verbatim}
NOT
\begin{verbatim}
\[ e^{\pi i} = -1 \]

where $i=\sqrt{-1}.$ 
\end{verbatim}
in order to avoid having the word ``where'' indented as the
beginning of a new paragraph.

Use \verb|\left(| and \verb|\right)| to get parens that are the right size for whatever is inside them.

For a variable or function name consisting of more than one letter, use \verb|\mathit{func}| or \verb|\mathrm{func}|.  Otherwise, latex interprets this as $f*u*n*c$.

For angled brackets to denote tuples, use \verb|\langle| and \verb|\rangle|, not \verb|<| and \verb|>|.

\section{Text}

TeX assumes that a period ends a sentence unless it follows an uppercase letter.
Use \verb|Smith et al.\ claim|, not \verb|Smith et al. claim|.
At the end of a sentence, use \verb|consisting of an NP\@.|, not \verb|consisting of an NP.|.

``et al.'' is ``et al.'', not ``et. al.'' or ``et. al''

\chapter{Conclusion}

\bibliographystyle{plainnat}
\bibliography{references}

\appendix
\chapter{More stuff}


\end{document}



